---
title: "Eyetracking report"
author: Nick Hedger
output: 
  html_document: 
    keep_md: yes
---

# Index

| Section | Description | Status |
| --- | --- | --- |
| [Initial plot](#plot) | Initial plot of a single observers data |
| [Cleaning](#Cleaning) | Summary of data cleaning |
| [Window](#Window) | Time window analysis |
| [Timeseries](#Timeseries) | Time series analysis |
| [Switching Analysis ](#Switching) | Analysis of switching behavior |

***

<a id='plot'></a>
# Initial plotting.

Summary plot of horizontal gaze position for a single observer.

```{r content,fig.width=12,fig.height=6}
library(drake)
readd(PLOT)
```

***

<a id='Cleaning'></a>
# Cleaning summary

### Trackloss Summary.

Proportion trackloss for each observer.

```{r}
tsummary=readd(CLEANED_FRAME)
tapply(tsummary$trackloss_summary$TracklossForParticipant,tsummary$trackloss_summary$ps,mean)
```


### Applied trackloss criteria.

The following trackloss criteria were applied. We excluded data from participants with more than `r tsummary$criteria[1]` % trackloss and trials with more than `r tsummary$criteria[2]` % trackloss


### Percentage of data removed due to trackloss.

Using the above criteria `r tsummary$perc_removed` % of the data were removed.

*** 

<a id='Window'></a>
# Time window analysis.

Ascertain whether participants looked longer at one AOI versus another.

### Model summary
```{r}
windowsummary=readd(WINDOW_FRAME)

summary(windowsummary$model)
```

### Main effects.
```{r}
windowsummary$modelp
```

### Interactions.

```{r}
windowsummary$interactions
```

### Plot

```{r}
windowsummary$PLOT
```


### Demographic variables - models.


```{r}
window_env=windowsummary

response_window_agg_by_sub=window_env$FRAME

modlist=ls(window_env)[str_detect(ls(window_env), 'modelp')]

for (i in 1:length(modlist)){
  print(get(modlist[i],window_env))
  
}

```


### Demographic variables - plots (not currently working).

```{r}

#modlist=ls(window_env)[str_detect(ls(window_env), 'modeld')]

#for (i in 1:length(modlist)){
#eff=allEffects(get(modlist[i],window_env))
#effframe=data.frame(get(ls(eff)[1],eff))
#effframe$var=get(sub("modeld", "", modlist[i]),effframe)

#x=ggplot(effframe,(aes(x=var,y=fit)))+geom_line(aes(colour=AOI),size=2)+facet_grid(.~sc)+geom_errorbar(aes(ymin=lower,ymax=upper,colour=AOI),size=1,width=3)+ scale_colour_manual(values = c("springgreen3","steelblue2"))+ scale_fill_manual(values = c("springgreen3","steelblue2"))+theme_classic()+ylab("Gaze Proportion")+theme(legend.position = "top")+xlab(sub("modeld", "", modlist[i]))
#print(x)

#}
```


*** 

<a id='Timeseries'></a>
# Time series Analysis.

Look at the timeseries of gaze bias.

### Plot of social bias as a function of time.

```{r}
ts=readd(TS_FRAME)

ts$TSPLOT

```


### Divergence analysis

When is the gaze bias into the social AOI significant?

```{r}
plotlist=ls(ts)[str_detect(ls(ts), 'TBPLOT')]
modlist=ls(ts)[str_detect(ls(ts), 'TBA')]

for (i in 1:length(plotlist)){
print(get(plotlist[i],ts))
summary(get(modlist[i],ts))
}

```


### Time bin analysis - demographic variables.

At what points in time do the demographic variables predict gaze to the social AOI?

```{r}
tsdem=readd(TS_DEMO_FRAME)

plotlist=ls(tsdem)[str_detect(ls(tsdem), 'clustplot')]
modlist=ls(tsdem)[str_detect(ls(tsdem), 'clustfit')]
modlist2=ls(tsdem)[str_detect(ls(tsdem), 'divfit')]

plotlist2=ls(tsdem)[str_detect(ls(tsdem), 'divplot')]


for (i in 1:length(plotlist)){ 
multiplot(get(plotlist2[i],tsdem),get(plotlist[i],tsdem),cols=2)
summary(get(modlist[i],tsdem))
summary(get(modlist2[i],tsdem))
}


```


*** 

<a id='Switching'></a>
# Switching analysis

### Overall switching behavior

How quickly to observers switch from an initially fixated AOI?

```{r}
switch=readd(TS_SWITCH_FRAME)
print(switch$modelp)

multiplot(switch$plotswitchall,switch$plotonseswitchall)

```


### Demographics


```{r}
plotlist1=ls(switch)[str_detect(ls(switch), 'dplotswitch')]
plotlist2=ls(switch)[str_detect(ls(switch), 'dplotonsetswitch')]

modlist=ls(switch)[str_detect(ls(switch), 'dmodelp')]


for (i in 1:length(plotlist)){ 
multiplot(get(plotlist1[i],switch),get(plotlist2[i],switch),cols=2)
print(get(modlist[i],switch))
}

```
